---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Sean Ryan**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```
covid_data_count |> 
  filter(state == "NJ") |> 
  ggplot(aes(x = date, y = Deaths, color = race)) + geom_line()
```
Looking at this plot I observed that in New Jersey, as time progressed, death rates generally increased for all races however the data shows that white people had a more drastic increase in deaths over time compared to other races.

2. Are there any conclusions you can draw?

From this plot it's difficult to draw any definitive conclusions but the data supports that for some unknown reason that deaths of white people were increasing at a higher rate than other races.

3. What were you not able to do due to not having the R knowledge?

Make the graph trend over a specific date range to get more detailed insight into the increasing death rates of Covid victims

4. What other data would be useful to better understand this data?

Other data that would be useful would be the proportion of people of each race that got Covid and the rates at which those Covid cases resulted in death cases.
